Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2017-02-01 Master Thesis/synopsis.tex
Use \longrightarrow

Let $K$ be a (not necessarily finitely generated) field over $\mathbb{Q}$ and dimension $2$.

@@

\begin{lemma}\label{2.4-finitelygenerated}
Let $K$ be finitely generated and $\ell\neq 2$ be a prime. The following map, induced by the restrictions, is injective:
\[ \mathrm{H}^3(K,\mathbb{Z}/\ell\mathbb{Z})\to\prod_{w\in |\operatorname{Spv}(K)| }\mathrm{H}^3(K_w,\mathbb{Z}/\ell\mathbb{Z}) \]
\end{lemma}

@@

\begin{proof}
We adopt the notation from the previous proof. First, we shall prove that the following map is injective for every model $\mathfrak{X}$ of $K$:
\[ f: \mathrm{H}^3(K) \to \prod_{y\in\mathfrak{X}_0}\mathrm{H}^3(K_y) \]
For $x\in\mathfrak{X}$ let $\mathcal{O}_x$ be a henselization of $\mathcal{O}_{\mathfrak{X}, x}$ and $K_x$ its quotient field. For $y\in\mathfrak{X}_0$ set $P_y=\operatorname{Spec}(\mathcal{O}_y)_1$. For $z\in P_y$ let $\mathcal{O}_z$ be a henselization of $\mathcal{O}_y$ at $z$ and $K_z$ its quotient field. For $y\in\mathfrak{X}_0$ and $x\in\mathfrak{X}_1$ let $P_{x,y}$ be the subset of $P_y$ consisting of all $z\in P_y$ which are mapped to $x$ under $\operatorname{Spec}(\mathcal{O}_y)\to\mathfrak{X}$. Consider the following commutative diagram:
\[ \begin{tikzcd}
\mathrm{H}^3(K)\ar[r, "\varphi"]\ar[d, "f"'] & \displaystyle\prod_{x\in\mathfrak{X}_1}\mathrm{H}^3(K_x)\ar[d, "\psi"]\\
\displaystyle\prod_{y\in\mathfrak{X}_0}\mathrm{H}^3(K_y) \ar[r, "g"']& \displaystyle\prod_{\substack{x\in\mathfrak{X}_1 \\ y\in\mathfrak{X}_0}}\prod_{z\in P_{x,y}}\mathrm{H}^3(K_z)
\end{tikzcd} \]
According to [Sa], Theorem (2-15) $g$ is injective. Now, $\psi\circ\varphi$ can be identified with the injective map $\Phi$ from the proof of the previous Lemma. Thus its image is contained in $\bigoplus\mathrm{H}^3(K_w)$. Therefore, $f$ is injective as well and its image is contained in $\bigoplus\mathrm{H}^3(K_y)$. Now, one easily checks that:
\[ \operatorname{supp}(f) = \bigcap_{\mathfrak{X}\in \mathfrak{M}(K)} \pi_\mathfrak{X}^{-1}(\{ y\in\mathfrak{X}_0\mid \operatorname{res}_{K_y/K}(f)\neq 0 \}) \]
Note that the right set is closed in $\operatorname{Spv}(K)$.
\end{proof}

\begin{lemma}[\textit{Main Lemma}]\label{2.4}
Let $K$ be not necessarily finitely generated and $\ell\neq 2$ be a prime. The following map, induced by the restrictions, is injective:
\[ \mathrm{H}^3(K,\mathbb{Z}/\ell\mathbb{Z})\to\prod_{w\in |\operatorname{Spv}(K)| }\mathrm{H}^3(K_w,\mathbb{Z}/\ell\mathbb{Z}) \]
\end{lemma}

>>>>

Let $K$ be a (not necessarily finitely generated) field over $\mathbb{Q}$ and of dimension $2$.

@@

\begin{lemma}\label{2.4-finitelygenerated}
Let $K$ be finitely generated and $\ell\neq 2$ be a prime. The following map, induced by the restrictions, is injective:
\[ \mathrm{H}^3(K,\mathbb{Z}/\ell\mathbb{Z})\longrightarrow\prod_{w\in |\operatorname{Spv}(K)| }\mathrm{H}^3(K_w,\mathbb{Z}/\ell\mathbb{Z}) \]
\end{lemma}

@@

\begin{proof}
We adopt the notation from the previous proof. First, we shall prove that the following map is injective for every model $\mathfrak{X}$ of $K$:
\[ f: \mathrm{H}^3(K) \longrightarrow \prod_{y\in\mathfrak{X}_0}\mathrm{H}^3(K_y) \]
For $x\in\mathfrak{X}$ let $\mathcal{O}_x$ be a henselization of $\mathcal{O}_{\mathfrak{X}, x}$ and $K_x$ its quotient field. For $y\in\mathfrak{X}_0$ set $P_y=\operatorname{Spec}(\mathcal{O}_y)_1$. For $z\in P_y$ let $\mathcal{O}_z$ be a henselization of $\mathcal{O}_y$ at $z$ and $K_z$ its quotient field. For $y\in\mathfrak{X}_0$ and $x\in\mathfrak{X}_1$ let $P_{x,y}$ be the subset of $P_y$ consisting of all $z\in P_y$ which are mapped to $x$ under $\operatorname{Spec}(\mathcal{O}_y)\to\mathfrak{X}$. Consider the following commutative diagram:
\[ \begin{tikzcd}
\mathrm{H}^3(K)\ar[r, "\varphi"]\ar[d, "f"'] & \displaystyle\prod_{x\in\mathfrak{X}_1}\mathrm{H}^3(K_x)\ar[d, "\psi"]\\
\displaystyle\prod_{y\in\mathfrak{X}_0}\mathrm{H}^3(K_y) \ar[r, "g"']& \displaystyle\prod_{\substack{x\in\mathfrak{X}_1 \\ y\in\mathfrak{X}_0}}\prod_{z\in P_{x,y}}\mathrm{H}^3(K_z)
\end{tikzcd} \]
According to [Sa], Theorem (2-15) $g$ is injective. Now, $\psi\circ\varphi$ can be identified with the injective map $\Phi$ from the proof of the previous Lemma. Thus its image is contained in $\bigoplus\mathrm{H}^3(K_w)$. Therefore, $f$ is injective as well and its image is contained in $\bigoplus\mathrm{H}^3(K_y)$. Now, one easily checks that:
\[ \operatorname{supp}(f) = \bigcap_{\mathfrak{X}\in \mathfrak{M}(K)} \pi_\mathfrak{X}^{-1}(\{ y\in\mathfrak{X}_0\mid \operatorname{res}_{K_y/K}(f)\neq 0 \}) \]
Note that the right set is closed in $\operatorname{Spv}(K)$.
\end{proof}

\begin{lemma}[\textit{Main Lemma}]\label{2.4}
Let $K$ be not necessarily finitely generated and $\ell\neq 2$ be a prime. The following map, induced by the restrictions, is injective:
\[ \mathrm{H}^3(K,\mathbb{Z}/\ell\mathbb{Z})\longrightarrow \prod_{w\in |\operatorname{Spv}(K)| }\mathrm{H}^3(K_w,\mathbb{Z}/\ell\mathbb{Z}) \]
\end{lemma}
